Markowitz Portfolio Optimization with Inflation

### 2023-11-01 paper/paper.tex
[PAPER] Introduce explored asset classes

>>>>

\section{Asset Classes}

For an asset class to offer protection against inflation, the asset returns have to be positively correlated with the CPI (Consumer Price Index) when we assume that only long positions can be held; so, when the CPI increases, the asset returns should also increase. The approach we present will be based on filtering. Starting from a large pool of potential assets that could hedge against inflation, we want to understand what are the assets that are more prone to have a positive relationship with inflation. That means analyzing the yearly inflation rates, and see what are the subsequent returns of a given class. We therefore expect that besides high correlation with inflation, when inflation is very high, returns also should be very high (tail inflation corresponds with the tail of returns). We test the following asset classes and sectors for a hedge against inflation:

\begin{itemize}
    \item XHB: Median Sale Price of Houses Sold in the United States
    \item CPIAUCSL: Consumer Price Index for All Urban Consumers
    \item DCOILWTICO: Crude Oil Prices: West Texas Intermediate (WTI)
    \item GSPC: S\&P 500 Index
    \item GC=F: Gold Futures
    \item GS10: 10-Year Treasury Constant Maturity Rate
    \item GS30: 30-Year Treasury Constant Maturity Rate
    \item VNQ: REITs (Vanguard Real Estate ETF)
    \item DBC: Commodities (Invesco DB Commodity Index Tracking Fund)
    \item FXE: Foreign Currencies (Currency Shares Euro Trust)
    \item BTC-USD: Cryptocurrencies (Bitcoin)
    \item IGF: Infrastructure Funds (iShares Global Infrastructure ETF)
    \item XLE: Energy Stocks (Energy Select Sector SPDR Fund)
\end{itemize}
